---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readgrads

<!-- badges: start -->
<!-- badges: end -->

The goal of readgrads is to provide functions to read and manipulate binay data files from the Grid Analysis and Display System ([GrADS](http://cola.gmu.edu/grads/)).

This repo is a fork of https://bitbucket.org/paulhiemstra/readgrads/src/default/ from Paul Hiemstra. 

The main changes made were to:

- obtain data in a `data.frame` including dates. This improvement was made using the gridt.r script by Marcos Longo (@mpaiao)


- allow importing binary files with specified extension ('.gra', '.bin') (parameter `file.ext` in the `readGradsFile()` function)

- specify the variables of interest in a new argument (varname in the `readGradsFile()` function)

## Installation

You can install the development version of readgrads from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("lhmet/readgrads")
```
## Example

This is a basic example which shows you how to use readgrads.

```{r example}
library(readgrads)
## basic example code
data_tmp <- tempfile(fileext = ".bin")
download.file(
  "http://ftp.cptec.inpe.br/modelos/io/produtos/MERGE/2019/prec_20191201.bin",
  data_tmp
)
ctl_tmp <- file.path(dirname(data_tmp), gsub(".bin", ".ctl", basename(data_tmp)))
download.file(
  "http://ftp.cptec.inpe.br/modelos/io/produtos/MERGE/2019/prec_20191201.ctl",
  ctl_tmp
)
x <- readGradsFile(
  data_tmp,
  file.ext = ".bin",
  convert2dataframe = TRUE,
  varname = "prec"
)
head(x)
```




